Analysis of Turkey's Trade with Selected Countries

### 2018-12-26 Final/PresentationFinal.Rmd
.

```{r, fig.align='center', fig.height=4.5, fig.width=6}
export_Product_Group <- export_jTableMELTED%>%
group_by(Country,PcodeTwo,X__2,year)%>%
summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Export_Quantity = Quantity,Export_Value =Values)

>>>>

```{r, fig.align='center', fig.height=4.5, fig.width=5}
export_Product_Group <- export_jTableMELTED%>%
group_by(Country,PcodeTwo,X__2,year)%>%
summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Export_Quantity = Quantity,Export_Value =Values)
